---
title: Predictive Modeling with NLP
author: Ezra Citron
date: '2021-05-30'
slug: []
categories: ['topic modeling','NLP']
tags: []
description: ~
featured_image: ~
draft: true
---
For a while I thought it'd be fun to apply natural language processing (NLP) techniques on artists lyrics - and see what it comes up with, whether the analysis chimes with our experience of listening to the artist.

Picking a rapper would be a good choice, purely because they give us more words than other artists. 

I'm going to split this out into a 5 series of blog posts, each focusing on different aspects of NLP.
- Predictive modeling with NLP
- Network structure 
- Topic analysis with NLP

```{r setup, echo = F}
knitr::opts_chunk$set(echo = FALSE,cache = T,warning = F,error = F, message = F)
```

```{r}
library(tidyverse)
```

```{r}
lyrics_raw <- read_csv('lyrics.csv')
```
 
```{r}
lyrics <- lyrics_raw %>% 
  mutate(year = str_extract(album,"(?<=\\()\\d+(?=\\))"), #get the year from album
         album = str_remove(album," \\(\\d+\\)")) # remove the year from album

```

```{r}
lyrics
```


make a feature of earlier/ later albums
```{r feature_engineering, echo =T}

lyrics <- lyrics %>% 
  mutate(age = if_else(year < 2015,'Older','Newer') )

```

How are Eminems later works different

```{r}

colour_pal <- RColorBrewer::brewer.pal(n = 3,name = 'Pastel1')

lyrics %>% 
  distinct(.keep_all = T,album) %>% 
  group_by(year) %>% 
  summarise( albums =paste(album,collapse = '   ')) %>% 
  ggplot(aes(y = as.Date(paste0(year,'-01-01') ),
             x = 0.01))+
  geom_rect(fill =colour_pal[1],
            aes(xmin = 0,xmax = 1.,
                ymin = as.Date('1995-01-01'),
                ymax = as.Date('2015-06-01')))+
    geom_rect(fill = colour_pal[3],
            aes(xmin = 0,xmax = 1.,
                ymin = as.Date('2015-06-01'),
                ymax = as.Date('2021-01-01')))+
  geom_text(aes(label = albums),hjust = 0,size = 5)+
  labs(y = 'Date')+
  scale_y_date(name = NULL,date_breaks = '5 year', 
               limits = c( as.Date('1995-01-01'),
                           as.Date('2021-01-01') ),
               date_labels = "%Y",expand = c(0,0))+
  scale_x_continuous(name = NULL,expand = c(0,0))+
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.length.y = unit(4,'mm'))
```

 
## Topic Modeling 
 
```{r}

library(stm)
library(quanteda)
library(tidytext)
lyrics_tokenised <- lyrics %>% 
  unnest_tokens(output = 'word',input = lyrics,token = 'words')

custom_stop_words <- tidytext::stop_words

lyrics_tokenised <- lyrics_tokenised %>% 
  anti_join(custom_stop_words,by = 'word')

# top words used
lyrics_tokenised %>% 
  count(word,sort=T) %>% 
  slice_head(n=20) %>% 
  mutate(word = fct_reorder(word,.x = n)) %>% 
  ggplot(aes(n,word,fill = n))+
  geom_col(show.legend = F)

# top words by album

lyrics_tokenised %>% 
  count(album,word,sort=T) %>% 
  group_by(album) %>% 
  slice_head(n=5) %>%
  ungroup() %>% 
  mutate(word = fct_reorder(word,.x = n)) %>% 
  ggplot(aes(n,word,fill = n))+
  geom_col(show.legend = F)+
  facet_wrap(vars(album),scales = 'free',ncol = 3)

```
 
 
## TF-IDF Between Albums
 TF-IDF is term frequency inverse document frequency. This translates to, "Does a word come up in this album significantly more than in comes up in others". The word "The" for example, will probably come up a lot in the album infinite, however, it'll come up a lot in the rest of the albums too, so won't have a high TF-IDF. However, **give an example**
 
 ## Sentiment over time
 
 
## predictive modelling for older and newer albums

```{r}
library(textfeatures)

lyrics_featues <- textfeatures::textfeatures(lyrics$lyrics)
lyrics <- lyrics %>% bind_cols(lyrics_featues) 

```


```{r}
library(tidymodels)

set.seed(123)
lyrics_split <- rsample::initial_split(lyrics,strata = age)

lyrics_train <- training(lyrics_split)
lyrics_test <- testing(lyrics_split)

```

```{r recipe}

#recipe(lyrics_train, age ~ . ) %>% 
#  recipes::step

```

