---
title: Automation using python-pptx
author: Ezra
date: '2021-05-10'
slug: []
categories: ['python', 'automation', 'powerpoint']
tags: ['a tag']
description: ~
featured_image: ~
draft: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE,error = FALSE,message = FALSE)
```


Automate Power point generation.
Here's the problem, you are are asked to run some analysis and generate a report for a population.
You produce some great work, creating some really stylish works that answers all all the questions and tells a great story. Then comes the inevitable "... and what does this look like for the US only..."

In this blog i'll show you how to automate creating sub reports in powerpoint. We'll use this  employee dataset which you can find it on [kaggle](www.google.com). Each row is a new person in the company and we are given given information such as where the employee is married, thier ethncity, thier pay and how satisfied they are as employees. 

I'm going to produce a mock report  of all 311 employees, and then automate the generation of separate sub-reports for each department.

First things first, lets read it the data.
```{r}
library(tidyverse)
library(ggplot2)
library(kableExtra)
headcount <- read_csv('../../../static/data/HRDataset_v14.csv')
DT::datatable(
  headcount %>% select(Employee_Name,ManagerID,RaceDesc,Salary),
  class = 'cell-border stripe'
  ) 
```

There are 6 departments, so these will be our final sub-reports
```{r}
headcount %>% 
  count(Department)
```

number of married
```{r include=FALSE}
headcount %>% 
  ggplot(aes(MarriedID))+
  geom_bar()
```

distribution of salary
```{r include=F}
headcount %>% 
  ggplot(aes(Salary))+
  geom_histogram()
```

ethnicity
```{r include=F}
headcount %>% 
  ggplot(aes(RaceDesc))+
  geom_bar()+
  coord_flip()
```

employee satisfaction

```{r include=F}
headcount %>% count(EmpSatisfaction) %>%
  ggplot(aes(x = 1, y = n,fill = EmpSatisfaction))+
  geom_col()
  # geom_text(aes(y = cumsum(n),label = (n)))
```


```{python}
# from pptx import Presentation
# import pandas as pd
# print(type(r.df))

```

